---
title: "SQMB Formative Assessment 1"
author: "EXAM NUMBER"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r attach-pkgs}
# Add the necessary packages here

```


# Instructions

This is a guided assessment that walks your through a basic data exploration pipeline with the main aim of producing a set of relevant plots.

Follow this template to complete the assignment. Be careful with your coding style and formatting.

The data for this assessment are taken from this study: https://ling.auf.net/lingbuzz/006708.
The study looked at the "locative impersonal", i.e. *everywhere* in sentences like:

1. Is eating fish and chips a regional thing? No, these days *everywhere* in Britain eats fish and chips!
2. When Chinese food first reached Europe, people used a knife and fork, but *everywhere* in Europe eats Chinese food using chopsticks these days.

The study collected acceptability ratings of those type of sentences, using an acceptability scale from 1 to 7 (a Likert scale).

Skim through Sections 1-3 of the paper linked above for an overview of the study.

In this assignment, you will have to make some plots of a selection of the data from the study.

# Import data

First import the data. Remember to attach the necessary packages in the code chunk above.

```{r read-data}

```

The data frame contains 25 columns. These are the main ones:

- `Value` in the data contains the acceptability ratings.
- `Restrictor` specifies if the sentence contained a restrictor for the impersonal locative.
  - RESTRICTED: Everywhere in Britain eats fish and chips!
  - NON_RESTRICTED: Everywhere eats fish and chips!
- `Condition` indicates which further syntactic condition the specific trial was from.
`gold-good` and `gold-bad` are control sentences that should elicit high and low acceptability ratings respectively. The other levels of `Condition` are the experimental conditions.

# Summarise data

# Plot

