---
title: "SQMB Formative Assessment 1"
author: "EXAM NUMBER"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r attach-pkgs}
# Add the necessary packages here

```


# Instructions

This is a guided assessment that walks your through a basic data exploration pipeline with the main aim of producing a set of relevant plots.

Follow this template to complete the assignment. Be careful with your coding style and formatting.

The data for this assessment are taken from this study: https://ling.auf.net/lingbuzz/006708.
The study looked at the "locative impersonal", i.e. *everywhere* in sentences like:

1. Is eating fish and chips a regional thing? No, these days *everywhere* in Britain eats fish and chips!
2. When Chinese food first reached Europe, people used a knife and fork, but *everywhere* in Europe eats Chinese food using chopsticks these days.

The study collected acceptability ratings of those type of sentences, using an acceptability scale from 1 to 7 (a Likert scale).

Skim through Sections 1-3 of the paper linked above for an overview of the study.

In this assignment, you will have to make some plots of a selection of the data from the study.

# Import data

First import the data. Remember to attach the necessary packages in the code chunk above.

```{r read-data}

```

The data frame contains 25 columns. These are the main ones:

- `Value` in the data contains the acceptability ratings.
- `Restrictor` specifies if the sentence contained a restrictor for the impersonal locative.
  - `0` non-restricted: *Everywhere eats fish and chips!*
  - `1` restricted: *Everywhere in Britain eats fish and chips!*
- `Condition` indicates which further syntactic condition the specific trial was from.
  - `gold-good` and `gold-bad` are control sentences that are expected to elicit high and low acceptability ratings respectively.
  - The other levels of `Condition` are the experimental conditions.

Mutate the values of the `Restrictor` column so that `0` becomes `non_restricted` and `1` becomes `restricted`. Can you think why this is better than using `0` and `1`?

```{r}

```


# Summarise data

Now calculate summaries measures for `Value`, `Restrictor` and `Condition` and any other column you like. Also, count occurrences of `Value` across `Restrictor` and `Condition`, separately and combined.

```{r}

```


# Plot

Produce the following plots. For each, write a brief description of the plot and patterns you notice in the plot.

## Plot 1

Create a simple plot which shows the total **counts** of each value in `Value`.

```{r}

```

Describe the plot.

## Plot 2

Create a plot that shows the counts for each `Value` depending on `Restrictor`.

```{r}

```

Describe the plot.

## Plot 3

Now add `Condition` to the mix with `Values` and `Restrictor`.
You can pick any specific solution (colour/fill, faceting, etc...).

```{r}

```

Describe the plot.

## Plot 4

Now create a last plot that includes any of the remaining columns in the data.

```{r}

```

Describe the plot.
